---
title: "Developing data products week 3 Assignment (R Markdown Presentation & Plotly)"
author: "Alemu Molla"
date: "January 24, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Instructions

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity!

## Installing Plotly

Installing Plotly is easy:

```r
install.packages("plotly")
library(plotly)
install.packages("ggplot2"")
library(ggplot2)
```

If you want to share your visualizations on https://plot.ly/ you should make an
account on their site.


## Read data sets for visualization
```r
Tmtcars<- data.frame(mtcars)
mtcars$am <- as.factor(mtcars$am)
transmission<- levels(mtcars$am) <- c("Automatic", "Manual")
mtcars$cyl<- as.factor(mtcars$cyl)
```

```{r, eval=FALSE}
library(plotly)
plot_ly(mtcars, x = ~wt, y = ~mpg, type = "scatter")
```

## Sample Vizualization

```{r, echo=FALSE, message=FALSE}
library(plotly)
plot_ly(mtcars, x = mtcars$wt, y = mtcars$mpg,
        mode = "markers", color = mtcars$am)
```

## Scatterplot Sizing

By specifying the `size` argument you can make each point in your scatterplot a
different size.

```{r, eval=FALSE}
plot_ly(mtcars, x = ~wt, y = ~mpg, type = "scatter", 
        color = ~factor(cyl), size = ~hp)
```

## Scatterplot Sizing

```{r, echo=FALSE, message=FALSE}
plot_ly(mtcars, x = ~wt, y = ~mpg, type = "scatter", 
        color = ~factor(cyl), size = ~hp)
```
